### 2022-05-27 main/chapter_2ljets.tex
cite mv2c10

Signal $b$-tagged jets require $\pt > 20\,\eV[G]$, $|\eta| < 2.5$ and a tag from
the `MV2c10' algorithm at its $77\%$ efficiency working point.
This tagging algorithm uses
\cite{atlas_jet_mv2c10_2017, atlas_jet_tagging_2019}
\TODO{cite, summarize}
%
boosted decision tree~\cite{friedman2002stochastic}

>>>>

Signal $b$-tagged jets require $\pt > 20\,\eV[G]$, $|\eta| < 2.5$ and a tag from
the `MV2c10' boosted decision tree
algorithm~\cite{
friedman2002stochastic,
atlas_jet_mv2c10_2017,
atlas_jet_tagging_2019
} at its $77\%$ efficiency working point, meaning that a true $b$-jet sampled
from the distribution of its $t\bar t$ testing set has a $77\%$ probability of
being tagged.
The `c10' suffix means that the its training data include a $7\%$ fraction of
$c$-jets~\cite{atlas_twiki_mv2}.

This tagging algorithm uses
\TODO{summarize}
